---
title: "Lab 00 - Hello IDS!"
author: "Ed Kimber"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Peter Rabbit", "Ed", "Keita", 
           "Helena", "Elsa"),
  github_username = c("mcgregors-garden", "edkimber", "n.a", 
                      "nouser", "notonhub"), 
  colour = c("powderblue", "navy", "black", 
             "gold", "maroon"),
  hobby = c("Hopping", "powerlifting", "sleeping", 
            "running", "singing"),
  favourite_number = c(2, 3, 4, 5, 7)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


It shows on graphs the people's answers to the questions

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Name", 
          y = "Number",
          title = "Favourite Number?")
```

It modifies axis, legend and plot labels.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

The data does not show who picked which hobby. A pie chart would be a better way to visualise it. 

